\problemname{Fljúgandi Furðuhlutir Forðast Fókus}
\illustration{0.5}{2572}{Image by Randall Munroe, \href{https://xkcd.com/2572/}{xkcd.com}}

As is well known, the Earth is of course flat and is monitored
by unscrupulous aliens who wish to make sure no one finds out
about this secret flatness. To this end the aliens must make
sure no one can get a clear picture of their spaceships.

The aliens thus maintain a database of where each individual
is located and the quality of their cameras.
From this they can calculate a minimum radius they have to
stay out of for any given individual. This however complicates
the aliens travel plans significantly. If too many individuals
obtain good cameras some travel plans might not just be slowed
down but made outright impossible. Can you help determine when
this occurs?
Because of the unusual alien spaceship design all travel plans
assume that the spaceships stay at a fixed height above the
ground.

\section*{Input}
The first line of input contains a positive integer $n$,
the number of individuals being monitored, and an integer
$h$, the height above the ground at which the spaceship stays.
Initially no one has a camera.
You may assume that $1 \leq n \leq 5 \cdot 10^4$ and $0 \leq h \leq 10^9$.
Next there are two lines describing the starting and desired
ending position of the spaceship, each given
by two integers giving the $x$ and $y$-coordinates,
respectively.
Next there are $n$ lines, each with two integers $x, y$.
The $i$-th line gives the coordinates of the $i$-th
individual.

Next there is a line with a single positive integer $m$,
the number of camera purchases.
You may assume $1 \leq m \leq 10^5$.
Then $m$ lines follow where the $i$-th line describes the $i$-th camera purchase.
Each line contains an integer $j_i$,
the index of the individual buying the camera,
and an integer $r_i$ giving the corresponding minimum radius
that the spaceship has to stay outside of.

The minimum radius for a given individual is always given
by the best camera they have access to.
You may assume $1 \leq j_i \leq n$ and $1 \leq r_i \leq 10^9$.
All coordinates in the input have a minimum value of
$10^{-9}$ and a maximum value of $10^9$.

\section*{Output}
If the $i$-th camera purchase blocks the spaceship from
being able to make it from the starting position to the
target position print $i$. If it is possible to travel 
between the starting and target location while staying outside of the cameras'
views after all camera purchases, instead print $-1$.
The purchases are made in the same order as they appear in the input.
