\problemname{Group Lockers}

\illustration{0.4}{lockers}{A set of lockers.}%
Sets of lockers can be found at different locations around the university. Each
set is arranged into columns of equal width, with between one and four lockers
in each column. At the start of each semester, students get the opportunity to
rent one of these lockers for the entire semester; this can be very handy for
students that would otherwise have to carry stacks of books between their
classes.

Upon hearing this, a group of $n$ friends decides that they each want their own
locker. None of them have any specific requirements about the size or location
of their locker, except that --- being such good friends --- they want their
lockers to be close to each other. In fact, they insist that all of their
lockers belong to the same set of lockers. Within that set, they want to
minimize the distance required to walk between the leftmost and rightmost
lockers that belong to the friends.

Given a candidate set of lockers, and the number of lockers that are available
for rent in each column, can you help the friends determine this distance if
they choose their $n$ lockers optimally?

\section*{Input}
The input consists of:
\begin{itemize}
    \item One line with two integers $n$ and $m$ ($1 \le n \le 10^9$, $1 \le m \le
    5\cdot 10^5$), the number of friends and the number of columns in the
    candidate set of lockers.
    \item One line with a string of $m$ digits $c_1c_2\ldots c_m$ ($0 \le c_i
    \le 4$), where $c_i$ represents the number of available lockers in column
    $i$.
\end{itemize}

\section*{Output}
Output the distance, measured in number of columns, required to walk between
the leftmost and rightmost lockers that belong to the friends, assuming they
rent the $n$ lockers that minimize this distance. If it is not possible to rent
$n$ lockers, output ``\texttt{impossible}''.

