\problemname{Kjördæmi Königsbergs}
\illustration{0.5}{2694}{Image by Randall Munroe, \href{https://xkcd.com/2694/}{xkcd.com}}

Königsberg, now known as Kaliningrad, is a city well known for its bridges.
Now bridges are to be built between the districts of the city to ensure travels around the city are possible.
Each bridge connects two districts of the city.

Building the bridges can be expensive and each bridge only immediately benefits the citizens of the two districts which the bridge connects.
Therefore, the funding for each half of a bridge comes from the two districts that build each half.
Sadly, inequality is prevalent in the city and not all districts have equal funding to spend on the bridges.
Note also that due to immense bureaucracy, all of the funding must be spent and therefore the exact number of bridges the funding covers must be built.

It is not important where each bridge leads to on its own.
However, after all bridges have been built it should be possible to travel by them around the entire city.
It is forbidden though to spend funds on two bridges which connect the same two districts.
It is also forbidden to spend funds on a bridge that connects a district to itself.
It can therefore prove difficult to connect the districts such that all bridges are built.

Can all the bridges be built such that the requirements are fulfilled?
If so, how should it be done?

\section*{Input}
Input consists of two lines.

The first line contains a single integer $n$, the number of districts in the city, where $1 \leq n \leq 100\,000$.
The second line consists of $n$ non-negative integers $d_1, \dotsc, d_n$, separated by spaces,
where $d_i$ represents the number of halves of bridges that district $i$ can afford to build.
It is guaranteed that the total number of bridges is at most $1\,000\,000$.

\section*{Output}
If the bridges cannot be built such that the requirements are satisfied you should output \texttt{"Omogulegt!"}.

Otherwise, you should first output a line consisting of two space separated integers $n$ and $m$, where $n$ is the number of districts and $m$ is the total number of bridges.
Then output $m$ lines, the $i$-th of which consists of two space separated integers, $a_i$ and $b_i$, denoting that a bridge should be built between districts $a_i$ and $b_i$.
Each pair of $a_i$ and $b_i$ must be distinct and must satisfy $a_i \neq b_i$, $1 \leq a_i \leq n$ and $1 \leq b_i \leq n$.

Note, the output can be \textbf{very large}, so it is advisable to use fast input and output methods.
