\problemname{Höskuldarháska}
\illustration{0.5}{2243}{Image by Randall Munroe, \href{https://xkcd.com/2243/}{xkcd.com}}

FKHÍ's continuous integration system performs many tasks.
Ensures input data is formatted correctly,
looks for typos in problem statements and more.
After having made a reference to a popular movie in the
last contest and spoiled an important plot point for those
who had not seen it yet, the organisers have decided to
add a spoiler filtering program into the integration system.
The spoiler filtering program should analyse all text in
the contest data files and make sure there is no text
spoiling important plot points that people would rather
not have spoiled. But to create such a system one needs
to determine what text is a spoiler, so the program knows
what it is looking for. Thus your task is to create a text
file containing all possible spoilers.

All possible first words of a spoiler have been determined,
same for all possible second words and so on.
Thus the only task left is to generate all possible 
combinations of these words to prepare the text file.

\section*{Input}

The input begins with a single integer $1 \leq n \leq 100$,
the number of words in each spoiler.
$n$ lines follow, one for each word.
The $i$-th line begins with an integer $1 \leq k \leq 100$,
the number of options for the $i$-th word.
Next these $k$ words follow on the same line, separated by
spaces. These $k$ words are distinct from each other.
All words in the input only contain English lower and upper
case characters.
Each word is at least $1$ letter and at most $20$ letters
in length.

\section*{Output}

Print all possible ways to combine the words into a spoiler.
Each spoiler should be on its own line.
The spoilers are to be printed in ASCII-order (note that this
is the default order in most programming languages).
It is guaranteed that the output will contain at most
$10^6$ letters.
