\problemname{Back to Studying}

The semester's final exams are approaching rapidly, but Arnar has yet to
begin studying. Instead he does what all other Computer Science students do
when exams are near: play video games all day long!

But now he's starting to get worried that he might not have enough time to
prepare for all of his exams. He knows the exam schedule, and for each exam he
knows how many days he must spend studying for the exam in order to pass. He
can only study for at most one exam per day, and he will not be able to do any
studying on days when there are exams.

Given this information, help Arnar determine if it is possible for him to study
enough to pass all his exams, and, in that case, how many additional days he
can spend playing video games before he has to begin studying.

\section*{Input}
The input consists of:
\begin{itemize}
    \item One line with one integer $n$ ($1 \le n \le 2\cdot 10^5$), the number
    of Arnar's final exams.
    \item $n$ lines, the $i$th of which contains two integers $d_i$ and $c_i$ ($1
    \le d_i, c_i \le 10^9$), the number of days before the $i$th exam and the
    number of days Arnar must study for this exam in order to pass.
\end{itemize}

There is at most one exam on any given day.

\section*{Output}
If there is no way for Arnar to spend the required number of days studying in
order to pass all his exams, output ``\texttt{impossible}''. Otherwise, output the
number of days Arnar can spend playing video games before he has to begin
studying in order to pass all his exams.

