\problemname{Austan Atlantshafs}
\illustration{0.5}{2901}{Image by Randall Munroe, \href{https://xkcd.com/2901/}{xkcd.com}}

Many cities and other institutions have a tendency to raise
statues of various kinds to garner attention.
In this context larger statues are of course preferable,
as a larger statue garners more attention.
It is even better when the statue is the largest in a large
area around where it is raised.
Each such institution wants to advertise its statue as
``the largest statue in X'' where X is the largest named
area which makes the statement true.
For example if a statue were the largest in all of Europe,
it would be a far better advertisement to claim it is the
largest in all of Europe rather than it being the largest
in Iceland, even though that would also be true if the
statue were located in Iceland.
Note that if, for example, Germany and France had equally
large largest statues, neither of them would be the largest
in all of Europe.

\section*{Input}
The first line of input contains a single integer $n$, the
number of named areas, satisfying $1 \leq n \leq 100\,000$.
Next there are $n$ lines, each describing one named area.
The $i$-th line contains a string $s_i$, a string $t_i$ and
a positive integer $x_i$, separated by spaces.
$s_i$ gives the name of the $i$-th area and $t_i$ gives the 
name of the area the $i$-th area is contained in.
$t_i$ is always one one of the areas named in the input.
$x_i$ then gives the height of the statue raised in the $i$-th area,
where $1 \leq x_i \leq 10^9$ if there is a statue in that area
and $x_i = -1$ otherwise.
If the area contains smaller areas $x_i = -1$ will hold, but
$x_i > 0$ otherwise.
No two different areas have the same name.

Each string in the input has length at most $20$ and
contains only lowercase English letters.
The total length of all strings in the input is at most
$10^6$.

The first area is always \texttt{jord}, which is given
to contain itself. 
No other area contains itself, directly or indirectly.

\section*{Output}
For each area with a statue, print the name of the largest
area such that the statue is the largest statue in that area.
An area is considered larger than another if it contains
the other area.
The names should be printed on separate lines, and given
in the same order as the input.
