\problemname{Lafhræddir Læknar}
\illustration{0.5}{2161}{Image by Randall Munroe, \href{https://xkcd.com/2161/}{xkcd.com}}

As the new hospital grows ever closer to finishing
construction the doctors get ever bolder. They have been
spotted past Gamla Hringbraut and even in the wetlands near
the airport. This worries both the University of Iceland
and University of Reykjavík. Clearly these doctors need to
be kept in check.

Luckily, as is well known, doctors can be kept at bay using
apples. More specifically keeping them at bay requires one
apple per doctor per day. Before this kind of issue could
be solved greedily, each doctor was given the weakest apple
that would still keep them at bay, and that was repeated for
each doctor each day. But now some doctors have developed
apple resistances which complicates matters quite a bit.

Given the apple resistances of the doctors and the apple
stash of the universities, can you find out for how many
days the doctors can be kept in check?

\section*{Input}
The first line of input contains two positive integers,
$L$ which gives the number of types of doctors and $E$
which gives the number of types of apples.
You may assume that $1 \leq L, E \leq 500$.
The next $E$ lines describe the types of apples.
Each line contains the name of the type, the strength
of the type and finally how many of that type the
universities have stashed away.
The strength is a positive integer less than or equal to $10^9$.
The universities also have a positive integer number of apples
stashed away of each type, and at most $10^9$ of any type.
Finally there are $L$ lines describing the types of doctors.
Each line contains the name of the type of doctor,
the strength of the type, the number of doctors of that type,
how many apple types that type is resistant to and finally
the names of those apple types.
As with the apples the strength and number are both positive
integers less than or equal equal to $10^9$.
Each type of doctor is resistant to at most $20$ types
of apples.
All names in the input are strings containing only lower
case ASCII characters with no spaces. All names are at most
$20$ characters in length. All names are unique.

\section*{Output}
Print the number of days the doctors can be held at bay.
That is to say if each doctor can be given $d$ apples
with a strength which is not lower than the doctor's strength
and the doctor is not immune to, but the same is not true for
$d + 1$, print $d$.
